### 2020-06-14 system-model.tex
:pencil: SWIPT-IRS review

	Most existing IRS SWIPT papers focus on narrow-band transmission and linear harvester model.

>>>>

	The effective channel enhancement and low power consumption of IRS are expected to bring more opportunities to SWIPT. Based on linear harvester model with energy interference, \cite{Wu2019b} proved that at most one energy beam is required to maximize the Weighted-Sum Power (WSP) subject to Signal-to-Interference-plus-Noise Ratio (SINR) constraints. The fairness issue was then considered in \cite{Tang2019}, which assumed perfect energy interference cancellation and maximized the minimum output power based on Alternating Optimization (AO) and Semi-Definite Relaxation (SDR) techniques. \cite{Wu2019c} proposed a novel penalty-based algorithm, whose inner layer employs Block Coordinate Descent (BCD) method to update precoders, phase shifts and auxiliary variables while the outer layer updates the penalty coefficients. It demonstrated that Line-of-Sight (LoS) links can boost the harvested power since the rank-deficient channels are highly correlated such that one energy stream is enough for all ERs. In \cite{Pan2019a}, the WSR maximization of MIMO SWIPT was first transformed to Weighted Minimum Mean Square Error (WMMSE) problem then solved by BCD with low-complexity iterative algorithms. However, most existing IRS-SWIPT papers focus on narrow-band transmission over linear harvester model.
